### 2014-10-17 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
San Francisco: Fix typo in caption

\begin{figure}[!ht]
\includegraphics[width=4.3in]{../Figures/SMV_Garage_Temp_340_s}
\input{../Figures/colorbar_metric_temp}
\input{../Figures/colorbar_std_temp}
\includegraphics[width=4.3in]{../Figures/SMV_Garage_Temp_352_s}
\input{../Figures/colorbar_metric_temp}
\input{../Figures/colorbar_std_temp}
\caption[Simulated temperature contours in the garage after basement window failure.]
{Top view of simulated temperature contours in the garage, 2~s before (top) and 10~s after (bottom) the first rear basement window failure.}
\label{fig:smv_flow_path_garage}
\end{figure}

>>>>

\begin{figure}[!ht]
\includegraphics[width=4.3in]{../Figures/SMV_Garage_Temp_340_s}
\input{../Figures/colorbar_metric_temp}
\input{../Figures/colorbar_std_temp}
\includegraphics[width=4.3in]{../Figures/SMV_Garage_Temp_352_s}
\input{../Figures/colorbar_metric_temp}
\input{../Figures/colorbar_std_temp}
\caption[Simulated temperature contours in the garage after basement window failure.]
{Simulated temperature contours in the garage, 2~s before (top) and 10~s after (bottom) the first rear basement window failure.}
\label{fig:smv_flow_path_garage}
\end{figure}
